A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-02-05 README.Rmd
some more info about the directory structure in the readme

This repository contains text, code and data for the paper. Further
context information can be found there.

The rendered document can be downloaded
[here](https://github.com/nevrome/cultrans.bronzeageburials.article2019/blob/document/article.pdf).

>>>>

This repository contains text, code and data for the paper. The paper is rendered via continuous integration and can be downloaded from the [document branch](https://github.com/nevrome/cultrans.bronzeageburials.article2019/tree/document), so
[here](https://github.com/nevrome/cultrans.bronzeageburials.article2019/blob/document/article.pdf).

The `analysis` directory contains `code` and `data` to reproduce the preparations, calculations, simulations and figure renderings in this paper. The `article` directory contains the tex template and the text for the paper in *.Rmd* format.
